\bf Forecasts Reconciliation: A geometric view with new insights on bias correction.

### 2019-08-17 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
first draft intro

	The past decade has seen rapid development in methodology for forecasting time series that adhere to linear aggregation constraints.  Of particular prominence have been {\em forecast reconciliation} methods involving two steps; first separate forecasts are produced for all series, then these are adjusted ex post to ensure coherence with the linear constraints.  Forecast reconciliation has mostly been formulated as a regression model, see \cite{Hyndman2011} and \cite{WicEtAl2019} for examples.  This setup can be counter-intuitive since a vector of forecasts coming from different time series models is also assumed to be the dependent variable in a regression model.  In this paper, we eschew a regression interpretation in favour of a novel, geometric understanding of forecast reconciliation.  In doing so, we review and provide clearer insight into existing approaches, and achieve a clearer understanding of the interplay between forecasts bias and reconciliation methods.

	Multivariate time series that follow an aggregation structure arise in many disciplines such as manufacturing, engineering, marketing and medicine\todo{include references}. Forecasts of these series should adhere to aggregation constraints to ensure aligned decision making. Earlier studies achieved this by only forecasting a single level of the hierarchy and then either aggregating in a bottom up fashion \citep{Dunn1976} or disaggregating in a Top-down \citep{Gross1990, Athanasopoulos2009} fashion.  For reviews of these approaches see \citet{Schwarzkopf1988, Kahn1998, Lapide1998, Fliedner2001}.

	In contrast to these approaches \cite{Hyndman2011} proposed forecasting all series in the hierarchy, referring to these as {\em base} forecasts.  Since base forecasts were produced independently they were not guaranteed to adhere to aggregation constraints and could be improved via further adjustment.  A framework was proposed whereby the forecasts were assumed to follow a regression model.  The predicted values from this model were guaranteed to adhere to the linear constraints by construction and could thus be used as a new set of forecasts.  This approach and later modifications have subsequently been shown to outperform bottom up and top down approaches in a variety of empirical settings\todo{references}.

	Some theoretical insight into the good performance of forecast reconciliation methods has been provided by \cite{VanErven2015a} and \cite{WicEtAl2019}.  Both papers provide a proof that reconciliation is guaranteed to improve base forecasts.  The latter paper also proposes a particular version of reconciliation known as the Minimum Trace (MinT) method.  This is optimal in the sense of minimising the trace of reconciled forecast error covariance matrix under the assumption that base forecasts are unbiased.

	While reviewing the existing studies in this literature, our attempt is to give a new understanding to the whole hierarchical forecasting problem with a geometric intuition. We first provide a geometric interpretation of coherency and reconciliation in terms of projections. Then we rehash all existing reconciliation methods into a single framework based on projections. In addition to being highly intuitive, this allows us to establish new theoretical results. We prove two new theorems about point forecast reconciliation, the first showing that reconciled forecasts dominate unreconciled forecasts via the distance reducing property of projections while the second shows that reconciliation via projections preserves the unbiasedness of base forecasts.

	Unbiasedness of base forecasts is a strong assumption in many of the existing methods which will be limited only to a selective number of forecasting methods. We propose a simple solution to this barrier. That is to correct the bias in base forecasts before doing the projection-based reconciliation. This allows using any advanced statistical method despite the unbiasedness to produce base forecasts without worrying about the unbiasedness. Using an empirical study, we further show that the reconciled forecasts follow from biased corrected base forecasts will improve the forecast accuracy compared to that of the biased forecasts.

	The remainder of this paper is structured as follows. In Section~\ref{sec:CoheForecasts} coherent point forecasting is defined geometrically while section~\ref{sec:Reconciliation} contains definitions of projection-based reconciliation as well as our main theoretical results. Section~\ref{sec:BiasInRecon} discuss the unbiased preserving property of projection-based reconciliation and Section \ref{sec:BiasCorrection} contains our proposed method to correct the bias in base forecasts. In Section \ref{sec:EmpStudy} we apply these methods to get coherent forecasts for domestic tourism flow in Australia and Section~\ref{sec:conclusions} concludes with some discussion and thoughts on future research.  
\section{Coherent forecasts}\label{sec:CoheForecasts}

>>>>

	The past decade has seen rapid development in methodology for forecasting time series that follow a hierarchical aggregation structure.  Of particular prominence have been {\em forecast reconciliation} methods involving two steps; first separate forecasts are produced for all series, then these are adjusted ex post to ensure coherence with the linear constraints.  Forecast reconciliation has mostly been formulated using a regression model, see \cite{Hyndman2011} and \cite{WicEtAl2019} for examples.  This setup can be counter-intuitive since a vector comprised of forecasts from different time series models is also assumed to be the dependent variable in a regression model.  In this paper, we eschew a regression interpretation in favour of a novel, geometric understanding of forecast reconciliation.  In doing so, we review and provide clearer insight into existing approaches, and achieve a clearer understanding of the interplay between forecasts bias and reconciliation methods.

	Multivariate time series following an aggregation structure arise in many disciplines such as manufacturing, engineering, marketing and medicine\todo{include references}. Forecasts of these series should adhere to aggregation constraints to ensure aligned decision making. Earlier studies achieved this by only forecasting a single level of the hierarchy and then either aggregating in a bottom up fashion \citep{Dunn1976} or disaggregating in a Top-down \citep{Gross1990, Athanasopoulos2009} fashion.  For reviews of these approaches including a discussion of their advantages and disadvantages see \citet{Schwarzkopf1988, Kahn1998, Lapide1998, Fliedner2001}.

	In contrast to these approaches \cite{Hyndman2011} proposed forecasting all series in the hierarchy, referring to these as {\em base} forecasts.  Since base forecasts were produced independently they were not guaranteed to adhere to aggregation constraints and could thus be improved via further adjustment.  A framework was proposed whereby the base forecasts were assumed to follow a regression model.  The predicted values from this model were guaranteed to adhere to the linear constraints by construction and could thus be used as a new set of forecasts.  This approach and later modifications have subsequently been shown to outperform bottom up and top down approaches in a variety of empirical settings\todo{references}.

	Some theoretical insight into the performance of forecast reconciliation methods has been provided by \cite{VanErven2015a} and \cite{WicEtAl2019}.  Both papers provide a proof that reconciliation is guaranteed to improve base forecasts.  The latter paper also proposes a particular version of reconciliation known as the Minimum Trace (MinT) method.  This is optimal in the sense of minimising the trace of reconciled forecast error covariance matrix under the assumption that base forecasts are unbiased.

	Our main contribution is to propose a geometric interpretation of the entire hierarchical forecasting problem.  In this setting, we show that reconciled forecasts will have a number of attractive properties when they are obtained via projections.  We believe that this is clearer and more intuitive than explanations based on regression modelling, notwithstanding the fact that most popular existing methods are indeed projections.  As such, this paper is in part a review of existing results cast in a new light, one that we believe to be warranted as forecast reconciliation methodologies becomes more popular.  However, we also propose three major and novel results.

	First, our approach makes it clear that the defining characteristic of so-called {\em hierarchical time series} is not aggregation but linear constraints.  As a result forecast reconciliation can be applied in contexts where there are no clear candidates of {\em bottom level} series, an insight that is not apparent when the problem is viewed through the lens of regression modelling.  Second, we provide a new proof that reconciled forecasts dominate unreconciled forecasts which makes explicit the link between a reconciliation method and a loss function.  We believe that this link is lacking in previous work that attempt to establish similar results, in particular \cite{VanErven2015a} and \cite{WicEtAl2019}.  Futhermore, unlike \cite{VanErven2015a} and \cite{WicEtAl2019} our proof does not require an assumption about convexity.  Third, we revisit the issue of bias.  We prove that reconciliation using certain projection matrices will guarantee reconciled forecasts will be unbiased if base forecasts are also unbiased.  A natural question that arises is what to do in the case of biased reconciled forecasts.  Rather than addressing this issue by considering matrices that are not projections, we propose to bias-correct before reconciliation.  This is evaluated in an extensive empirical study where we find that even when bias correction fails, the extent of the problem is mitigated by reconciling forecasts.

	The remainder of this paper is structured as follows. Section~\ref{sec:CoheForecasts} deals with the concept of coherence and defines so called hierarchical time series in a way that does not depend on any notion of bottom level series.  Section~\ref{sec:Reconciliation} defines forecast reconciliation in terms of projection and includes our proof that reconciled forecasts is guaranteed to dominate base forecasts with respect to a specific loss function. In Section~\ref{sec:BiasInRecon} we prove the unbiasedness preserving property of reconciliation via certain projection matrices and propose method for bias correction. In Section \ref{sec:EmpStudy} we evaluate these methods for in an extensive emprirical application to domestic tourism flow in Australia.  Section~\ref{sec:conclusions} concludes with some discussion and thoughts on the  future of research in forecast reconciliation.  
\section{Coherent forecasts}\label{sec:CoheForecasts}
